Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-11-03 Draft/Draft1.7.tex
minor changes

\author{Xiao-Dong Li,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\author{Cristiano G. Sabiu,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Changbom Park,}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\author{Yuting Wang, Gong-bo Zhao}
\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
\author{Hyunbae Park, Arman Shafieloo,}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
\author{and Sungwook E. Hong}
\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}

@@

\begin{abstract}
We perform the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
to place constraints on the expansion history of the Universe.
We use the 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 12, 
spanning the redshift range $0.15<z<0.69$.
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We improve the methodology of Li et al. to enable efficient exploring of three or more cosmological parameters,
and apply it to the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a{z}/({1+z})$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ $ and $w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30 -- 40\%
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We check the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   The distance dependence of the shape distortion in four wrongly assumed cosmologies,
   assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   There are four perfect squares with their true shapes plotted in blue dashed lines.
   They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   The apparently distorted shapes are plotted in red solid lines.
   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=18cm]{fig_fan.eps}
   %\includegraphics[width=9.0cm]{fig_2pcf.eps}
   %\includegraphics[width=8.5cm]{fig_fan_2.eps}
   }
   \caption{\label{fig_fan}
   %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   A patch of SDSS BOSS DR12 galaxies in the fan shape region $\rm 140^\circ < RA < 170 ^\circ$, $\rm 10^\circ < DEC < 13 ^\circ$,
   split into six non-overlapping redshift bins (marked by the light green rings) in order to probing the redshift evolution of anisotropic clustering.
   In the left and right panels, we plot the galaxies positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
   and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
   Redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the edges of redshift bins are listed.
   %The shape of structures look different in these two cosmologies. 
   In the dynamical dark energy cosmology, we see relative stretch of structures compared with the $\Lambda$CDM cosmology.
   The stretch is not significant in the first redshift bin, and becomes large in high redshift bins.
   We use this phenomena to discover the AP effect and place constraints on cosmologies.
   %By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
   %we are able to distinguish different cosmologies.
   %The obtained galaxy distribution is different.
   %
   %The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   %The vertical dashed lines define the six redshift bins that are used to cut the samples.
   %The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   %Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
   %   in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
   % The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
   % The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are numerous and range from a non-zero  vacuum energy, an evolving  scalar  field  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity \citep{2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe allowing us to 
differentiate between competing models.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion \citep{Li2014} as a way of mitigating the RSD effect. 
The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
However, if cosmological parameters are incorrectly chosen and there exists the AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Figure \ref{fig_xy} shows how the shape distortion varies with distance, i.e., redshift, 
when incorrect cosmologies are used to infer distances).
In \cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2PCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=8.95cm]{fig_xi_cosmo1.eps}
   \includegraphics[width=8.95cm]{fig_xi_cosmo2.eps}
   }
   \caption{\label{fig_xi}
   $\hat\xi_{\Delta s}(\mu)$ measured from the SDSS BOSS DR12 galaxies in six redshift bins (three in LOWZ and three in CMASS),
   assuming the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11 $\Lambda$CDM.
   Measurements in the six redshift bins and their redshift evolution with respective to the first bin of LOWZ are plotted.
   In the $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
   and the amount of difference changes with redshift;
   a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
   indicating that it is not likely to be the underlying true cosmology of our universe.
   The measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology; plotted in green color)
   can match the shape of curves measured from real observational data, 
   indicating that the simulation well reproduces the FoG and Kaiser effects.
   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2PCFs (red dashed lines) 
   inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
   The error induced in the approximation procedure is very small.
   }
\end{figure*}

@@

Figure \ref{fig_xy} illustrates the AP effect in wrong cosmologies.
A redshift dependence of shape distortion is observed in case of adopting wrong values of $w_0$ and $w_a$,
thus we expect that these two parameters will be effectively constrained by our method.

@@

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covers a higher redshift ($0.4\lesssim z \lesssim 0.7$),
targeted to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The edges are determined so that the number of galaxies are roughly the same in different redshift bins 
(for LOWZ and CMASS samples, respectively).

@@

Figure \ref{fig_fan} shows a patch of 10,976 BOSS DR12 galaxies,
whose positions are computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology 
and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
The shape of structures look different in these two cosmologies. 
In the later cosmology, there is apparent stretch of structures, 
and the degree of compression becomes more significant in higher redshift bins.
By investigating how the anisotropy of galaxy distribution evolves in the six redshift bins,
we are able to distinguish this cosmology from the $\Lambda$CDM cosmology.

Following our previous methodology, the information of small-scale anisotropic clustering is computed as 
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
\begin{equation}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds,
\end{equation}
with $s_{\rm min}=6 h^{-1} {\rm Mpc},$ and $s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalize these {\em clustering shells} as 
\begin{equation}
\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}
\end{equation}
to nullify the amplitude information of the clustering signal, 
which is not associated with the AP test and is mostly sensitive to the galaxy bias.
%The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
%The contour lines are not horizontal due to the effects of peculiar velocity,
%and the RSD effect clearly manifest itself through the tilting of contour lines.
%However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects as
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use a number of $n_{\mu}$=20, 21, ... 25 bins for the value of $\hat\xi_{\Delta s}(\mu)$ at $0<\mu<\mu_{\rm max}$.
For the removal of fiber collision and the strong finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.

Systematics effects are estimated using mock catalogues derived from Horizon Run 4 \citep[HR4;][]{HR4},
an N-body simulation with a box size of $L={3150}$ $h^{-1}$Mpc, the number of particles $6300^3$,   
initial redshift of $z_{i}=100$, and the WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
%As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
%(mainly comes from redshift evolution of RSD and galaxy bias)
%reaches 4 -- 6\% at the highest redshift bin,
%and is minor ($\lesssim2\%$) at the other redshift bins.

The covariance matrix, ${\bf Cov}$, is computed from the 2,000 sets of MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

@@

\begin{figure*}
   \centering{
   \includegraphics[width=8.5cm]{fig_IO.eps}
   \includegraphics[width=8.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_Check}
 Left panel: Input-output test of the AP methodology using four sets of BOSS DR12 galaxy mock catalogues constructed from the HR4 simulation.
 The approximate 2PCFs are adopted in the analysis.
 The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology
 (the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM; marked by the black plus).
 Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
 (i.e., the value of $w_a$ fixed as zero).
 Results obtained using the precise 2PCFs (cyan filled) 
 and approximate 2PCFs (red dashed) agree with each other quite well.
   }
\end{figure*}

As an illustration,
Figure \ref{fig_xi} shows how we us the above procedure to distinguish different cosmologies.
Here we plot the value of $\hat\xi_{\Delta s}(\mu)$, as long as its redshift evolution, 
measured from the BOSS DR12 galaxies in six redshift bins.
Two $\Lambda$CDM cosmologies are adopted, 
one with $\Omega_m=0.26$, and the other with obviously wrong value of $\Omega_m=0.11$.

The shape of $\hat \xi_{\Delta s}(\mu)$ is far away from a flat curve, 
due to the apparent anisotropy produced by the peculiar motion of galaxies.
In the $\Omega_m=0.11$ cosmology, 
the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the measurements in the $\Omega_m=0.26$ cosmology,
and the amount of difference systematically evolves with redshift.
So we observe a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$, 
indicating that it is not likely to be the underlying true cosmology of our universe.

>>>>

%[Xiao-Dong~Li, Cristiano G. Sabiu, Yuting Wang, Changbom~Park, Gong-bo Zhao, Hyunbae Park, Arman Shafieloo, Juhan Kim and Sungwook E. Hong]
\author{Xiao-Dong~Li$^{1,2}$, Cristiano G. Sabiu$^3$, Yuting Wang$^4$, Changbom~Park$^2$, Gong-bo Zhao$^4$, Hyunbae Park$^3$, Arman Shafieloo$^3$, Juhan Kim$^5$ and Sungwook E. Hong$^3$}
%{ Xiao-Dong Li$^{1,2,\dagger}$, Changbom Park$^{1}$, Cristiano G. Sabiu$^{2}$, Juhan Kim$^{3,1,\star}$, Sungwook E. Hong$^{1}$\\
\affil{$^1$School of Physics and Astronomy, Sun Yat-Sen University, Guangzhou 510297, P.R.China}
\affil{$^2$School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
\affil{$^3$Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
\affil{$^4$National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
\affil{$^5$Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}

%\author{Xiao-Dong Li,}
%\affil{School of Physics and Astronomy, SYSU TBA}
%\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
%\author{Cristiano G. Sabiu,}
%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
%\author{Changbom Park,}
%\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 02455, Korea}
%\author{Yuting Wang, Gong-bo Zhao}
%\affil{National Astronomy Observatories, Chinese Academy of Science, Beijing, 100012, P.R.China}
%\author{Hyunbae Park, Arman Shafieloo,}
%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}
%\author{Juhan Kim,}
%\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 02455, Korea}
%\author{and Sungwook E. Hong}
%\affil{Korea Astronomy and Space Science Institute, 776, Daedeokdae-ro, Yuseong-gu, Daejeon, 34055, Korea}

@@

\begin{abstract}
We derive tight constraints on dynamical dark energy 
from the Alcock-Paczynski (AP) test via the redshift dependence of clustering on scales of 6 -- 40 $h^{-1}\rm Mpc$
to place constraints on the expansion history of the Universe.
We use the 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 12, 
spanning the redshift range $0.15<z<0.69$.
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
We improve the methodology of Li et al. to enable efficient exploring of three or more cosmological parameters,
and apply it to the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a{z}/({1+z})$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ $ and $w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30 -- 40\%
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We check the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[height=5cm]{fig_xy.eps}
   %\includegraphics[height=8cm]{fig4_1.eps}
   %\includegraphics[height=7cm]{FVol.eps}
   %\includegraphics[height=8cm]{xy.eps}
   %\includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_xy}
   %The distance dependence of the shape distortion in four wrongly assumed cosmologies,
   %assuming a true cosmology of $\Omega_m=0.26$, $w=-1$.
   %There are four perfect squares with their true shapes plotted in blue dashed lines.
   %They are measured by an observer located at the origin, and the distances are reprojected in the four wrong cosmologies.
   %The apparently distorted shapes are plotted in red solid lines.
   Examples of the rectangular shape distorted by assuming incorrect 
   cosmologies compared to the true fiducial cosmology $\Omega_m=0.26$ and $w=-1$.
   The blue dashed boxes mark the reference rectangular shape
   and the red distorted boxes are the shapes observed at the coordinate origin.
   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=18cm]{fig_fan.eps}
   %\includegraphics[width=9.0cm]{fig_2pcf.eps}
   %\includegraphics[width=8.5cm]{fig_fan_2.eps}
   }
   \caption{\label{fig_fan}
   %We split the BOSS DR12 galaxies into six redshift bins to measure the evolution of shape distortion.
   A patch of SDSS BOSS DR12 galaxies in the fan shape region of 
   $\rm 140^\circ < R.A. < 170 ^\circ$, $\rm 10^\circ < Decl. < 13 ^\circ$,
   split into six non-overlapping redshift bins (marked by the light green arcs) in order to probe the redshift evolution of anisotropic clustering.
   In the left and right panels, we plot the galaxy positions computed in two cosmologies: the $\Omega_m$=0.26 $\Lambda$CDM, 
   and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
   Redshifts and comoving distances (in unit of $h^{-1}\rm Mpc$) of the edges of redshift bins are listed.
   %The shape of structures look different in these two cosmologies. 
   In the dynamical dark energy cosmology, we see relative stretch of structures compared with the $\Lambda$CDM cosmology.
   The stretch is not significant in the first redshift bin, and becomes large in high redshift bins.
   We use this apparent distortion to discover the AP effect and place constraints on cosmologies.
   %By investigating how the anosotropy of galaxy distribution evolves in the six redshift bins,
   %we are able to distinguish different cosmologies.
   %The obtained galaxy distribution is different.
   %
   %The blue and green solid histograms show the redshift density distribution of LOWZ and CMASS galaxies in the $\Omega_m=0.31$ $\Lambda$CDM. 
   %The vertical dashed lines define the six redshift bins that are used to cut the samples.
   %The number of LOWZ/CMASS galaxies in the three low/high redshift bins are listed.
   %Right panel: 2D contour map of measured $\xi$ as a function of $\mu$ and $s$, from the six redshift bins of LOWZ and CMASS samples, 
   %   in the cosmology of $\Omega_m=0.31$ $\Lambda$CDM model.
   % The black dashed lines mark the clustering region 6-40\ Mpc/h studied in the AP method.
   % The six contour maps have rather similar appearance, implying small redshift evolution of $\xi$ from RSD.
   }
\end{figure*}

The  origin  of  the late-time accelerating  expansion  of  the  universe  is  one of  the  most  salient  questions  in  contemporary cosmology. 
Theoretical explanations for this phenomena are numerous and range from a non-zero  vacuum energy, an evolving  scalar  field  remnant  from  the  big  bang, 
to modifications of Einstein's General Relativity \citep{Li2011,2012IJMPD..2130002Y}. 
Considering the wealth of theoretical explanations, 
it is crucial to obtain precise and unbiased measurements of the expansion history of the Universe which allows us to 
differentiate between competing models.

@@

Previously, we proposed to use the {\it redshift dependence} of the AP distortion \citep{Li2014} as a way of mitigating the RSD effect. 
The clustering anisotropies produced by RSD are, although large, close to uniform in magnitude over a wide range in redshift.  
However, if cosmological parameters are incorrectly chosen and there exists the AP effect, 
the anisotropy in the clustering signal has a clear redshift dependence
(as an illustration, Figure \ref{fig_xy} shows how the shape distortion varies with distance 
when incorrect cosmologies are used to infer distance from redshift).
In \cite{Li2015}, we developed an AP methodology 
that utilizes the redshift dependence of the galaxy 2-point correlation function (2PCF), 
measured as a function of angle between the galaxy pair and line-of-sight (LoS).

\begin{figure*}
   \centering{
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{figCPL_a.pdf}
   \includegraphics[width=8.95cm]{fig_xi_cosmo1.eps}
   \includegraphics[width=8.95cm]{fig_xi_cosmo2.eps}
   }
   \caption{\label{fig_xi}
   $\hat\xi_{\Delta s}(\mu)$ measured from the SDSS BOSS DR12 galaxies in six redshift bins (three in LOWZ and three in CMASS),
   assuming the $\Omega_m=0.26$ $\Lambda$CDM cosmology and a more dark energy dominated cosmology, $\Omega_m=$0.11 $\Lambda$CDM.
   Measurements in the six redshift bins and their redshift evolution with respective to the first bin of LOWZ are plotted.
   In the $\Omega_m$=0.11 cosmology, the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the $\Omega_m=0.26$ cosmology results,
   and the difference changes with redshift;
   a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$ is detected in this cosmology, 
   indicating that it is not likely to be the underlying true cosmology of our universe.
   The measurements in the HR4 mock catalogues (always in the $\Omega_m=0.26$ $\Lambda$CDM cosmology; plotted in green color)
   match the shape of curves measured from observational data, 
   indicating that the simulation well reproduces the FoG and Kaiser effects.
   For the $\Omega_m$=0.11 cosmology, we also plot the approximate 2PCFs (red dashed lines) 
   inferred using the technique described in Sec. \ref{sec:approx_2pcf}.
   The error induced in the approximation procedure is very small.
   }
\end{figure*}

@@

Figure \ref{fig_xy} illustrates the AP effect in wrong cosmologies.
A redshift dependence of shape distortion is observed in case of adopting wrong values of $w_0$ and $w_a$,
thus we expect that these two parameters will be effectively constrained by our method.
There is a fare degree of degeneracy in the resulting expansion history
between increasing $w_0$ and adopting similar $w_0$ but increased $w_1$.

@@

The spectroscopic galaxy sample of SDSS-III BOSS (Baryon Oscillation Spectroscopic Survey) has two primary catalogues:
%the LOWZ at $z\leq0.4$, and CMASS covering $0.4\leq z \leq 0.7$. %of galaxies.
the LOWZ sample, designed as an extension of the SDSS-I/II luminous red galaxy sample to $z\approx 0.4$ and fainter luminosities,
and the CMASS sample covering a higher range ($0.4\lesssim z \lesssim 0.7$),
and made to be an approximately stellar mass limited sample of massive, luminous galaxies \citep{Reidetal:2016}.
In the clustering analysis we use 1,133,326 galaxies, split into six, non-overlapping redshift bins, 
$0.150<z_1<0.274<z_2<0.351<z_3<0.430<z_4<0.511<z_5<0.572<z_6<0.693$.
The edges are determined so that the number of galaxies are roughly the same in different redshift bins 
(for LOWZ and CMASS samples, respectively).

@@

Figure \ref{fig_fan} shows a patch of 10,976 BOSS DR12 galaxies,
whose positions are computed in the $\Omega_m$=0.26 $\Lambda$CDM cosmology 
and a dynamical dark energy cosmology with $\Omega_m=0.26,\ w_0=-1,\ w_a=-2$.
The shape of structures look different in these two cosmologies. 
In the latter cosmology, there is apparent stretch of structures, 
and the degree of compression becomes more significant in higher redshift bins.
By investigating how the anisotropy of galaxy distribution evolves in the six redshift bins,
we are able to distinguish this cosmology from the $\Lambda$CDM cosmology.

Following our previous methodology, the information of anisotropic clustering is computed as 
%\footnote{These correlations were computed using the public code \texttt{KSTAT} \citep{kstat}.} 
\begin{equation}
\xi_{\Delta s} (\mu) \equiv \int_{s_{\rm min}}^{s_{\rm max}} \xi (s,\mu)\ ds,
\end{equation}
with $s_{\rm min}=6 h^{-1} {\rm Mpc},$ and $s_{\rm max}=40 h^{-1} {\rm Mpc}$.
We then normalize these {\em clustering shells} as 
\begin{equation}
\hat\xi_{\Delta s}(\mu) \equiv \frac{\xi_{\Delta s}(\mu)}{\int_{0}^{\mu_{\rm max}}\xi_{\Delta s}(\mu)\ d\mu}
\end{equation}
to nullify the amplitude information of the clustering signal, 
which is not associated with the AP test and is mostly sensitive to the galaxy bias evolution.
%The right panel of Figure \ref{fig_TpCF} shows the contour map of $\xi(s,\mu)$ measured in the six redshift bins.
%The contour lines are not horizontal due to the effects of peculiar velocity,
%and the RSD effect clearly manifest itself through the tilting of contour lines.
%However, the shape of the tilted lines remain similar at different redshifts, a fact that enables us  to mitigate the RSD effect by focusing on the redshift dependence of the anisotropic clustering signal.
The ``correct'' cosmological model is selected by minimizing the amount of redshift evolution of $\hat\xi_{\Delta s}$,
via a $\chi^2$ function of 
\begin{equation}
 \chi^2\equiv \sum_{i=2}^{6} \sum_{j_1=1}^{n_{\mu}} \sum_{j_2=1}^{n_{\mu}} {\bf p}(z_i,\mu_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,\mu_{j_2})
\end{equation}
where ${\bf p}(z_i,\mu_{j})$ is the redshift evolution of clustering with respect to the lowest redshift bin,
while subtracting systematic effects as
\begin{eqnarray}
 {\bf p}(z_i,\mu_{j}) \equiv\ & \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right] \\ \nonumber
 &- \left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}.
\end{eqnarray}
We use $n_{\mu}$=20, 21, ... 25 bins for the value of 
$0<\mu<\mu_{\rm max}$.
To reduce the fiber collision and the finger of god (FoG) effect \citep{FOG} near the LOS we take a cut $\mu_{\rm max} = 0.97$.

The systematics effects are estimated using mock catalogues drawn from Horizon Run 4 \citep[HR4;][]{HR4},
an N-body simulation with a box size of $L={3150}$ $h^{-1}$Mpc, the number of particles $6300^3$,   
initial redshift of $z_{i}=100$, and the WMAP5\citep{komatsu2011} cosmological parameters 
$(\Omega_{b},\Omega_{m},\Omega_\Lambda,h,\sigma_8,n_s)$  = (0.044, 0.26, 0.74, 0.72, 0.79, 0.96). 
Mock galaxy samples are produced using a modified version of the one-to-one correspondence scheme \citep{hong2016}. 
%As presented in \cite{Li2016}, the value of $\left[\hat\xi_{\Delta s}(z_i,\mu_j)-\hat\xi_{\Delta s}(z_1,\mu_j)\right]_{\rm sys}$
%(mainly comes from redshift evolution of RSD and galaxy bias)
%reaches 4 -- 6\% at the highest redshift bin,
%and is minor ($\lesssim2\%$) at the other redshift bins.

The covariance matrix, ${\bf Cov}$, is computed from the a set of 2,000 MultiDark PATCHY mock catalogues \citep{MDPATCHY}.
The statistical bias and scattering in the likelihood function (due to the finite number of mocks in covariance estimation) 
are adequately corrected \citep{Hartlap,Percival2014}.

@@

\begin{figure*}
   \centering{
   \includegraphics[width=8.5cm]{fig_IO.eps}
   \includegraphics[width=8.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_Check}
 Left panel: Input-output test of the AP methodology using four sets of BOSS DR12 galaxy mock catalogues constructed from the HR4 simulation.
 The approximate 2PCFs are adopted in the analysis.
 The inferred cosmological constraints from the method, shown in the cyan contours, are consistent with the input cosmology
 (the simulation cosmology, i.e. the $\Omega_m=0.26$ $\Lambda$CDM; marked by the black plus sign).
 Right panel: Cosmological constraints from the BOSS DR12 galaxies, assuming a $w$CDM cosmology 
 (i.e., the value of $w_a$ fixed as zero).
 Results obtained using the precise 2PCFs (cyan filled) 
 and approximate 2PCFs (red dashed) agree with each other quite well.
   }
\end{figure*}

{\bf TBA}
As an illustration,
Figure \ref{fig_xi} shows how we us the above procedure to distinguish different cosmologies.
Here we plot the value of $\hat\xi_{\Delta s}(\mu)$, as long as its redshift evolution, 
measured from the BOSS DR12 galaxies in six redshift bins.
Two $\Lambda$CDM cosmologies are adopted, 
one with $\Omega_m=0.26$, and the other with obviously wrong value of $\Omega_m=0.11$.

The shape of $\hat \xi_{\Delta s}(\mu)$ is very different from a flat curve, 
due to the apparent anisotropy produced by the peculiar motion of galaxies.
In the $\Omega_m=0.11$ cosmology, 
the shapes of $\hat\xi_{\Delta s}(\mu)$ are different from the measurements in the $\Omega_m=0.26$ cosmology,
and the amount of difference systematically evolves with redshift.
So we observe a large redshift evolution of $\hat\xi_{\Delta s}(\mu)$, 
indicating that it is not likely to be the underlying true cosmology of our universe.
